Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-11 methods_paper/fabl-paper.tex
update.

	{\centering \includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_trace}

	\caption{Traceplot for number of matches found across datasets in El Salvador case study}\label{fig:overlap_trace}
\end{figure}

	{\centering \includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_trace}

	\caption{Traceplot for m parameter in El Salvador case study}\label{fig:m_trace}
\end{figure}

	{\centering \includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/u_trace}

	\caption{Traceplot for u parameter in El Salvador case study}\label{fig:u_trace}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_trace} 
\caption{Traceplot for number of matches found across datasets in El Salvador case study}\label{fig:overlap_trace}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_trace} 
\caption{Traceplot for m parameter in El Salvador case study}\label{fig:m_trace}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/u_trace} 
\caption{Traceplot for u parameter in El Salvador case study}\label{fig:u_trace}
\end{center}
\end{figure}

\newpage
\bigskip
